Template for ACM CCS 2017

### 2018-07-08 main-sketch.tex
use ccs template

\input{macros}

\title{\textbf{Notes of DP - Bayesian Inference}\\}
% \author{Jiawen \textsc{Liu}}
\date{\vspace{-10ex}}

\begin{document}
\maketitle

@@

\subsection{Algorithm Setting up}
We define a new mechanism $\hexpmech(x)$
which is similar to the exponential mechanism where we use
$\mathcal{R}$ as the set $\betaset$ of beta distributions with integer parameters
summing up to $n+2$, as scoring function we use the Hellinger distance
from $\bysinfer(x)$, i.e. $\hlg(\bysinfer(x),-)$, and we 
calibrate the noise to the smooth sensitivity~\cite{nissim2007smooth}. The
only difference is in the sensitivity part, since now we use the
smooth sensitivity.

@@

\subsection{Sliding Property of Exponential Mechanism}
\begin{lem}
Consider the exponential mechanism  $\sexpmech(x,u,\mathcal{R})$
calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
\end{equation*}

\end{lem}

\begin{proof}

We denote the normalizer of the probability mass in $\hexpmech(x)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL(x)$:
\begin{equation*}
\begin{split}
LHS 
  = \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL(x)}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL(x)}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL(x)}\\
& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
\end{split}
\end{equation*}

By bounding the $\Delta \geq -S(x)$, we can get:

\begin{equation*}
\begin{split}
\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
\end{split}
\end{equation*}

\end{proof}

\subsection{Dilation Property of Exponential Mechanism}
\begin{lem}
for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:

\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.
\end{lem}

\begin{proof}

The sensitivity is always greater than 0, and our utility function $-\hlg(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

We set the $h(c) = Pr[u(\hexpmech(x)) = c] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL(x)}$.

We first consider $\lambda < 0$. In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(x)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(x)})}$ is at most $\frac{\epsilon}{2}$.

Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(x)) (1 - e^{\lambda})}{S(x)})$. Consider the event $G = \{ \hexpmech(x) : u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$. Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$. The probability of $G$ under density $h(c)$ is $1 - \frac{\delta}{2}$. Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta}{2}$.\\

@@

\end{proof}

\subsection{Privacy Analysis}
\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
\end{lem}

\begin{proof}
of Lemma \ref{lem_hexpmech_privacy}: For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z \in \mathcal{S}] + \delta. 
\end{equation*}
Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]$, let $\mathcal{U}_1 = \frac{u(y,z) - u(x,z)}{S(x)}$, $\mathcal{U}_2 = \mathcal{U} + \mathcal{U}_1$ and $\mathcal{U}_3 = \mathcal{U}_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$. Then,

\begin{equation*}
\begin{split}
2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
& = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
& \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
& \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
& = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \Big) + \delta\\
\end{split}
\end{equation*}

The first inequality holds by the sliding property, since the $\mathcal{U}_1 \geq -S(x)$. The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.

\end{proof}

@@

\begin{figure*}
\begin{center}
\centering
  \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1.eps}}
  \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
\caption{Accuracy measurement based on Hellinger distance wrt. different datasizes. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$}
\label{fig_vs_datasize}
\end{center}
\end{figure*}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{accuracy_vs_dimension}
\caption{Accuracy measurement based on Hellinger distance wrt. different dimensions and data size. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
\label{fig_vs_dimension}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{accuracy_vs_mean_1_1}
\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
\label{fig_vs_variance}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{accuracy_vs_prior_5_5_5}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data set is: $[5,5,5]$}
\label{fig_vs_prior}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{Accuracy_VS_Prior_mean.eps}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution and data variances. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
\label{fig_vs_prior_variance}
\end{figure}

@@

\bibliographystyle{plain}
\bibliography{bayesian.bib}

>>>>

\documentclass[sigconf, anonymous]{acmart}

\fancyhf{} % Remove fancy page headers 
\fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2017} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions
\acmConference[Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
\acmYear{2017}

\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions

%%\ccsPaper{9999} % TODO: replace with your paper number once obtained
\input{macros}

\begin{document}
\title{Template for ACM CCS 2017} % TODO: replace with your title

\begin{abstract}
Your abstract should go here. You will also need to upload a plain-text abstract into the web submission form.
\end{abstract}

% TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10003029.10011703</concept_id>
<concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
% -- end of section to replace with generated code

\keywords{template; formatting; pickling} % TODO: replace with your keywords

\maketitle

% \input{main-sketch} % TODO: replace with your brilliant paper!
% \input{macros}

@@

% \subsection{Algorithm Setting up}
We define a new mechanism $\hexpmech(x)$
which is similar to the exponential mechanism where we use
$\mathcal{R}$ as the set $\betaset$ of beta distributions with integer parameters
summing up to $n+2$, as scoring function we use the Hellinger distance
from $\bysinfer(x)$, i.e. $\hlg(\bysinfer(x),-)$, and we 
calibrate the noise to the smooth sensitivity~\cite{nissim2007smooth}. The
only difference is in the sensitivity part, since now we use the
smooth sensitivity.

@@

% \subsection{Sliding Property of Exponential Mechanism}
% \begin{lem}
% Consider the exponential mechanism  $\sexpmech(x,u,\mathcal{R})$
% calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
% \delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
% \begin{equation*}
% \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
% \leq
% e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
% \end{equation*}

% \end{lem}

% \begin{proof}

% We denote the normalizer of the probability mass in $\hexpmech(x)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL(x)$:
% \begin{equation*}
% \begin{split}
% LHS 
%   = \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
% & = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL(x)}\\
% & = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL(x)}\\
% & = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL(x)}\\
% & = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
% \end{split}
% \end{equation*}

% By bounding the $\Delta \geq -S(x)$, we can get:

% \begin{equation*}
% \begin{split}
% \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
% & \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
% &  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
% \end{split}
% \end{equation*}

% \end{proof}

% \subsection{Dilation Property of Exponential Mechanism}
% \begin{lem}
% for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:

% \begin{equation*}
% \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
% \leq
% e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
% \end{equation*}
% where the sensitivity in mechanism is still smooth sensitivity as above.
% \end{lem}

% \begin{proof}

% The sensitivity is always greater than 0, and our utility function $-\hlg(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

% We set the $h(c) = Pr[u(\hexpmech(x)) = c] = 2\frac{exp(\frac{\epsilon z}{2 S(x)})}{NL(x)}$.

% We first consider $\lambda < 0$. In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(x)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(x)})}$ is at most $\frac{\epsilon}{2}$.

% Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(x)) (1 - e^{\lambda})}{S(x)})$. Consider the event $G = \{ \hexpmech(x) : u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$. Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$. The probability of $G$ under density $h(c)$ is $1 - \frac{\delta}{2}$. Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta}{2}$.\\

@@

% \end{proof}

% \subsection{Privacy Analysis}
% \begin{lem}
% \label{lem_hexpmech_privacy}
% $\hexpmech$ is $(\epsilon, \delta)$-differential privacy.
% \end{lem}

% \begin{proof}
% of Lemma \ref{lem_hexpmech_privacy}: For all neighboring $x, y \in D^n$ and all sets $\mathcal{S}$, we need to show that:
% \begin{equation*}
% \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \leq e^{\epsilon} \underset{z \thicksim \hexpmech(y)}{Pr}[z \in \mathcal{S}] + \delta. 
% \end{equation*}
% Given that $2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big) = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]$, let $\mathcal{U}_1 = \frac{u(y,z) - u(x,z)}{S(x)}$, $\mathcal{U}_2 = \mathcal{U} + \mathcal{U}_1$ and $\mathcal{U}_3 = \mathcal{U}_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$. Then,

% \begin{equation*}
% \begin{split}
% 2\Big( \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}]\Big)
% & = \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}]\\
% & \leq e^{\epsilon / 2} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_2]\\
% & \leq e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ u(x,z) \in \mathcal{U}_3] + e^{\epsilon/2} \cdot \frac{\delta'}{2}\\
% & = e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(y)}{Pr}[ u(y,z) \in \mathcal{U}] + \delta = 2\Big( e^{\epsilon} \cdot \underset{z \thicksim \hexpmech(x)}{Pr}[ z \in \mathcal{S}] \Big) + \delta\\
% \end{split}
% \end{equation*}

% The first inequality holds by the sliding property, since the $\mathcal{U}_1 \geq -S(x)$. The second inequality holds by the dilation property, since $\frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)}) \leq 1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})}$.

% \end{proof}

@@

\begin{figure}[ht]
\begin{center}
\centering
  \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
    \includegraphics[width=0.35\textwidth]{accuracy_vs_datasize_1_1.eps}}
  \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
    \includegraphics[width=0.35\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
\caption{Accuracy measurement based on Hellinger distance wrt. different datasizes. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$}
\label{fig_vs_datasize}
\end{center}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{accuracy_vs_dimension}
\caption{Accuracy measurement based on Hellinger distance wrt. different dimensions and data size. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
\label{fig_vs_dimension}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{accuracy_vs_mean_1_1}
\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
\label{fig_vs_variance}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{accuracy_vs_prior_5_5_5}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data set is: $[5,5,5]$}
\label{fig_vs_prior}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{Accuracy_VS_Prior_mean.eps}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution and data variances. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
\label{fig_vs_prior_variance}
\end{figure}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{bayesian.bib}
